\documentclass[answers]{exam}

%% Language and font encodings
\usepackage[english]{babel}

\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,margin=2cm]{geometry}

%% Useful packages
\usepackage{amsmath, hyperref}
\usepackage{graphicx}
\usepackage{paralist, pgfplots}
%\setlength\FrameSep{4pt}






\pdfpagewidth 8.5in
 \pdfpageheight 11in


%General













%Theorem Environments

\begin{document}




\begin{center}
 \hfill Sandi Xhumari \\ \textbf{$\triangleright$ In-class Activity 6.0-6.2 Introduction to Differential Equations $\triangleleft$}\\
\end{center}


\textbf{Purpose:} Often times in real world applications we can determine relationships between the rates of change of various quantities, but we may have a hard time determining the quantities themselves. If we think of a quantity as a function, then we may determine equations relating its derivatives. So, are there ways to determine the function itself? This is the main focus of Differential Equations, a branch of math that is of utmost importance in applications. This handout's main goal is to introduce \\





\textbf{Knowledge/Skills and Criteria for Success:} After this activity you should be able to
\begin{enumerate}[A.]
\item Understand what differential equations and initial value problems are.
\item Check if a function is a solution to a differential equation.
\item Solve differential equations of the form $y\rq{} = f(x)$.
\item Be able to find anti-derivatives of common functions and use them to solve initial value problems.
\item 
\item 

\end{enumerate}

\textbf{Task:} 

\begin{questions}
\question Through experimentation, the acceleration $g$ due to gravity of a falling object on Earth is constant $-32$ ft/s$^2$ at any height. At time $t = 3$, a falling object had velocity $-10$ ft/s. What is the velocity of the object as a function of time in this case? Can we determine its position based on the given information?

\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break

\question A differential equation is an equation involving derivatives. Recall that to solve an equation in $x$ means to find all possible \emph{numbers} $x$ that fit the equation. To solve a differential equation involving the derivative(s) of $y$ means to find all possible \emph{functions} $y$ that fit the equation. Solve the following differential equations, and graph their slope fields.
\begin{enumerate}[(a)]
\item $\displaystyle y\rq{} = 2x$ 

\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break

\newpage


\item $\displaystyle \frac{dy}{dx} = y$

\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break

\end{enumerate}

\question Is $y = xe^{2x}+e^x$ a solution to the following differential equation?
\[ y''-4y'-4y=e^x \iff \frac{d^2y}{dx^2}-4\frac{dy}{dx} -4y = e^x \]

\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break


\question Solve the following initial value problems (IVP).

\begin{enumerate}[(a)]
\item Find $f(x)$ given $f\rq{}\rq{}(x) = \cos(x)$, with initial values $f\rq{}(0) = 3$ and $f(2) = 5$.

\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break



\item $\frac{dy}{dx} = \frac{9+13x}{xy^2}$ for $x>0$, with initial condition $y(1) = 4$.

\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break



\end{enumerate}

\question Suppose $f\rq{}(x) = 1/x^2$ and $f(1) = 1$. Then $f(-1) = 3$.
\begin{enumerate}[(a)]
\item True, and very confident.
\item True, but not confident.
\item False, and very confident.
\item False, but not confident.
\end{enumerate}

\end{questions}



\end{document}