\documentclass[answers]{exam}

%% Language and font encodings
\usepackage[english]{babel}

\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,margin=2cm]{geometry}

%% Useful packages
\usepackage{amsmath, hyperref}
\usepackage{graphicx}
\usepackage{paralist, pgfplots}
%\setlength\FrameSep{4pt}






\pdfpagewidth 8.5in
 \pdfpageheight 11in


%General













%Theorem Environments

\begin{document}


	\begin{center}
	\hfill Sandi Xhumari \\ \textbf{$\triangleright$ In-class Activity 7.3 $\triangleleft$}\\
\end{center}

\textbf{Purpose:} To get more practice on inverse trig integration techniques, and solve some optimization questions with trigonometric functions.  \\

\textbf{Knowledge/Skills and Criteria for Success:} After this activity you should be able to

\begin{enumerate}[A.]
	\item find anti-derivatives of rational functions with a linear polynomial in the denominator. 
	\item see where some of the trig formulas come from.
	\item consider some optimization questions related to Calculus 2.
	\item
	\item
	
\end{enumerate}

\textbf{Task:}


\begin{questions}


\question Use the fact that $\frac{d}{dx} \left(\sin^{-1}(x)\right) = \frac{1}{\sqrt{1-x^2}}$ to derive the formula we used in the previous handout for the following integral.\\
$\displaystyle \int \frac{1}{\sqrt{a^2-x^2}}dx = $
 
\vspace{2in }

\question Describe the general strategy to find the integral of a rational function with a degree one (linear) polynomial in the denominator. Consider the two cases: I) numerator is a constant, II) numerator is degree one or higher. Create an example for each case and solve it. 

\newpage


\question Imagine a river and highway perpendicular to each other as the $x$ and $y$ axis on a coordinate grid. Pick two points $A$ and $B$ on the first quadrant. What is the shortest path from $A$ to $B$ given that you need to go to the river and highway along the way? Think geometrically.
\vfill


\question Let $V(L)$ be the volume when the area between $f(x)=\sin(x)$  on $[0, 2\pi]$ is rotated around $y=L$.  Find the value of $L$ that minimizes $V(L)$.

\vfill



\end{questions}



\end{document}