\documentclass[answers]{exam}

%% Language and font encodings
\usepackage[english]{babel}

\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,margin=2cm]{geometry}

%% Useful packages
\usepackage{amsmath, hyperref}
\usepackage{graphicx}
\usepackage{paralist, pgfplots}
%\setlength\FrameSep{4pt}






\pdfpagewidth 8.5in
 \pdfpageheight 11in


%General













%Theorem Environments

\begin{document}


	\begin{center}
	\hfill Sandi Xhumari \\ \textbf{$\triangleright$ In-class Activity 8.3 $\triangleleft$}\\
\end{center}

\textbf{Purpose:} To learn the partial fractions technique of integrating. This technique helps us solve a lot of otherwise inaccessible integrals. \\

\textbf{Knowledge/Skills and Criteria for Success:} After this activity you should be able to

\begin{enumerate}[A.]
	\item solve integrals using the partial fractions technique.
	\item recognize when to use partial fractions versus other methods.
	\item
	\item
	
\end{enumerate}

\textbf{Task:}


\begin{questions}

\question Compute the following integrals. The first one is a hint for the second one.\\

\begin{enumerate}[(a)]
	\item $\displaystyle \int \frac{1}{3-x} - \frac{1}{x^2+9} dx =$\\
	
	\item $\displaystyle \int \frac{x^2+x+6}{-x^3+3x^2-9x+27} dx =$\\
	\vspace{.5in}
\end{enumerate}

\question The proper factors/divisors (i.e., excluding 1 and the number itself) of $24$ that are powers of primes are 
\vspace{0.5in}

\question What is the number of proper factors that are powers of irreducible polynomials of $(3-x)^4(x^2+9)^2$? Justify your answer by listing them out.
\begin{enumerate}[(a)]
	\item 6
	\item 2
	\item 13
	\item none of the above
\end{enumerate}

\question Partial fraction decomposition allows one to split a fraction into a sum of fractions with denominators that are proper factors of the original fraction denominator. The numerator is a general polynomial of degree one less than the degree of the irreducible factor in the denominator. Use partial fraction decomposition to find the following integrals. 

\begin{enumerate}[(a)]
	
	\item $\displaystyle \int \frac{x^2+x+6}{-x^3+3x^2-9x+27} dx =$\\
	
	\vspace{2in}
	
	\item $\displaystyle \int \frac{24}{x^2+x-2} dx =$\\
	
	\vspace{2in}
	
	\item $\displaystyle \int \frac{24}{(x-1)^2(x+2)} dx =$\\
	
	\vspace{2in}
	
	\item $\displaystyle \int \frac{x^4+6}{x^3+4x^2} dx =$

	\vspace{1in}
	

\end{enumerate}

\question Please write below any feedback you would like to share about this handout. If you found any parts confusing due to wording or anything like that, please suggest fixes. Thank you!

\end{questions}


\end{document}